### 2023-12-26 sections/4-results.tex
rearranged plots dir. broke supplement

\begin{figure}
    \begin{subfigure}[b]{0.47\textwidth}
    \includegraphics[width=0.95\textwidth]{images/lfd_plots/fashion-mnist-60000-lfd.png}\\
    \subcaption{Fashion-mnist}
    \label{fig:results:fashion-mnist-lfd}
    \end{subfigure}%
    \begin{subfigure}[b]{0.47\textwidth}
    \includegraphics[width=0.95\textwidth]{images/lfd_plots/glove-25-1183514-lfd.png}\\
    \subcaption{Glove-25}
    \label{fig:results:glove-25-lfd}
    \end{subfigure}
    \vspace{1em}
    \\
    \begin{subfigure}[b]{0.47\textwidth}
    \includegraphics[width=0.95\textwidth]{images/lfd_plots/sift-1000000-lfd.png}\\
    \subcaption{Sift}
    \label{fig:results:sift-lfd}
    \end{subfigure}%
    \begin{subfigure}[b]{0.47\textwidth}
    \includegraphics[width=0.95\textwidth]{images/lfd_plots/radio-ml-97920-lfd.png}\\
    \subcaption{RadioML}
    \label{fig:results:radioml-lfd}
    \end{subfigure}%
    \\
    \begin{subfigure}[b]{0.47\textwidth}
    \includegraphics[width=0.95\textwidth]{images/lfd_plots/silva-2224640-lfd.png}\\
    \subcaption{Silva 18S}
    \label{fig:results:silva-lfd}
    \end{subfigure}%  
    \begin{subfigure}[b]{0.47\textwidth}
    \includegraphics[width=0.95\textwidth]{images/lfd_plots/random-1000000-lfd.png}\\
    \subcaption{A random dataset}
    \label{fig:results:random-lfd}
    \end{subfigure}
    \vspace{1em}
    \caption{Local fractal dimension vs. cluster depth across six datasets, grouped by decile of local fractal dimension and weighted by the cardinalities of the clusters.
    The last dataset is randomly generated.
    {\color{red} TODO: Remove the headers from the plots themselves and rely on subcaptions instead.}}
    \label{fig:results:lfd-plots}
\end{figure}

>>>>

\begin{figure}
    \begin{subfigure}[b]{0.47\textwidth}
    \includegraphics[width=0.95\textwidth]{images/lfd/fashion-mnist-60000.png}\\
    \subcaption{Fashion-mnist}
    \label{fig:results:fashion-mnist-lfd}
    \end{subfigure}%
    \begin{subfigure}[b]{0.47\textwidth}
    \includegraphics[width=0.95\textwidth]{images/lfd/glove-25-1183514.png}\\
    \subcaption{Glove-25}
    \label{fig:results:glove-25-lfd}
    \end{subfigure}
    \vspace{1em}
    \\
    \begin{subfigure}[b]{0.47\textwidth}
    \includegraphics[width=0.95\textwidth]{images/lfd/sift-1000000.png}\\
    \subcaption{Sift}
    \label{fig:results:sift-lfd}
    \end{subfigure}%
    \begin{subfigure}[b]{0.47\textwidth}
    \includegraphics[width=0.95\textwidth]{images/lfd/radio-ml-97920.png}\\
    \subcaption{RadioML}
    \label{fig:results:radioml-lfd}
    \end{subfigure}%
    \\
    \begin{subfigure}[b]{0.47\textwidth}
    \includegraphics[width=0.95\textwidth]{images/lfd/silva-2224640.png}\\
    \subcaption{Silva 18S}
    \label{fig:results:silva-lfd}
    \end{subfigure}%  
    \begin{subfigure}[b]{0.47\textwidth}
    \includegraphics[width=0.95\textwidth]{images/lfd/random-1000000.png}\\
    \subcaption{A random dataset}
    \label{fig:results:random-lfd}
    \end{subfigure}
    \vspace{1em}
    \caption{Local fractal dimension vs. cluster depth across six datasets, grouped by decile of local fractal dimension and weighted by the cardinalities of the clusters.
    The last dataset is randomly generated.
    {\color{red} TODO: Remove the headers from the plots themselves and rely on subcaptions instead.}}
    \label{fig:results:lfd-plots}
\end{figure}

### 2023-12-26 supplement.tex
some edits
updated plots in supplement
rearranged plots dir. broke supplement

>>>>

\begin{figure}[ht!]
    \centering
    \includegraphics[width=3.4in]{plots/fashion-mnist-knn-100.png}
    \caption{
        Scaling behavior of algorithms on fashion-mnist with $k=100$. 
    }
    \label{fig:supplement:fashion-mnist-k-100}
\end{figure}

\begin{figure}[ht!]
    \centering
    \includegraphics[width=3.4in]{plots/sift-knn-100.png}
    \caption{
        Scaling behavior of algorithms on sift with $k=100$. 
    }
    \label{fig:supplement:sift-k-100}
\end{figure}

\begin{figure}[ht!]
    \centering
    \includegraphics[width=3.4in]{plots/glove-25-knn-100.png}
    \caption{
        Scaling behavior of algorithms on glove-25 with $k=100$. 
    }
    \label{fig:supplement:glove-25-k-100}
\end{figure}

\begin{figure}[ht!]
    \centering
    \includegraphics[width=3.4in]{plots/random-knn-100.png}
    \caption{
        Scaling behavior of algorithms on random with $k=100$. 
    }
    \label{fig:supplement:random-k-100}
\end{figure}

\begin{figure}[ht!]
    \begin{subfigure}[b]{0.47\textwidth}
    \includegraphics[width=0.95\textwidth]{images/radius/fashion-mnist-60000.png}\\
    \subcaption{Fashion-mnist}
    \label{fig:results:fashion-mnist-radius}
    \end{subfigure}%
    \begin{subfigure}[b]{0.47\textwidth}
    \includegraphics[width=0.95\textwidth]{images/radius/glove-25-1183514.png}\\
    \subcaption{Glove-25}
    \label{fig:results:glove-25-radius}
    \end{subfigure}
    \vspace{1em}
    \\
    \begin{subfigure}[b]{0.47\textwidth}
    \includegraphics[width=0.95\textwidth]{images/radius/sift-1000000.png}\\
    \subcaption{Sift}
    \label{fig:results:sift-radius}
    \end{subfigure}%
    \begin{subfigure}[b]{0.47\textwidth}
    \includegraphics[width=0.95\textwidth]{images/radius/radio-ml-97920.png}\\
    \subcaption{RadioML}
    \label{fig:results:radioml-radius}
    \end{subfigure}%
    \\
    \begin{subfigure}[b]{0.47\textwidth}
    \includegraphics[width=0.95\textwidth]{images/radius/silva-2224640.png}\\
    \subcaption{Silva 18S}
    \label{fig:results:silva-radius}
    \end{subfigure}%  
    \begin{subfigure}[b]{0.47\textwidth}
    \includegraphics[width=0.95\textwidth]{images/radius/random-1000000.png}\\
    \subcaption{A random dataset}
    \label{fig:results:random-radius}
    \end{subfigure}
    \vspace{1em}
    \caption{Radius vs. cluster depth across six datasets, grouped by decile of radius and weighted by the cardinalities of the clusters.
    The last dataset is randomly generated.}
    \label{fig:results:radius-plots}
\end{figure}

\begin{figure}[ht!]
    \begin{subfigure}[b]{0.47\textwidth}
    \includegraphics[width=0.95\textwidth]{images/fractal_density/fashion-mnist-60000.png}\\
    \subcaption{Fashion-mnist}
    \label{fig:results:fashion-mnist-fractal_density}
    \end{subfigure}%
    \begin{subfigure}[b]{0.47\textwidth}
    \includegraphics[width=0.95\textwidth]{images/fractal_density/glove-25-1183514.png}\\
    \subcaption{Glove-25}
    \label{fig:results:glove-25-fractal_density}
    \end{subfigure}
    \vspace{1em}
    \\
    \begin{subfigure}[b]{0.47\textwidth}
    \includegraphics[width=0.95\textwidth]{images/fractal_density/sift-1000000.png}\\
    \subcaption{Sift}
    \label{fig:results:sift-fractal_density}
    \end{subfigure}%
    \begin{subfigure}[b]{0.47\textwidth}
    \includegraphics[width=0.95\textwidth]{images/fractal_density/radio-ml-97920.png}\\
    \subcaption{RadioML}
    \label{fig:results:radioml-fractal_density}
    \end{subfigure}%
    \\
    \begin{subfigure}[b]{0.47\textwidth}
    \includegraphics[width=0.95\textwidth]{images/fractal_density/silva-2224640.png}\\
    \subcaption{Silva 18S}
    \label{fig:results:silva-fractal_density}
    \end{subfigure}%  
    \begin{subfigure}[b]{0.47\textwidth}
    \includegraphics[width=0.95\textwidth]{images/fractal_density/random-1000000.png}\\
    \subcaption{A random dataset}
    \label{fig:results:random-fractal_density}
    \end{subfigure}
    \vspace{1em}
    \caption{Fractal Density vs. cluster depth across six datasets, grouped by decile of fractal density and weighted by the cardinalities of the clusters.
    The last dataset is randomly generated.
    Fractal Density is defined as $\frac{cardinality}{radius^{LFD}}$}
    \label{fig:results:fractal_density-plots}
\end{figure}
